(Biological) Life-Cycle Algorithm\thanks{Supported by organization x.}

### 2021-07-15 history/paper_v2.tex
Abstract update
Work in progress.

Several bio-inspired algorithms use population evolution as analogies of
nature. In this paper, we followed a strategy that takes a similar approach as
the study of bacteria growth in microbiology, where using a microscope, we can
observe and analyze the evolution of a population over time. We present an
algorithm inspired by the biological life-cycle of animal species, which
consists of several stages: birth, growth, reproduction, and death. As in
nature, we intend to execute all these stages in parallel and asynchronously on
a population that evolves constantly. In this paper, we present a novel distributed nature-inspired algorithm for
solving optimization problems. From the ground up, we designed the algorithm as
a cloud-native solution using the cloud available resources to divide the
processing workload, among several computers or running the algorithm as a
cloud service. The algorithm works concurrently and asynchronously on a
constantly evolving population, using different computers (or containers)
independently, eliminating waiting times between processes. This algorithm 
seeks to imitate the natural life cycle, where new individuals
are born at any moment and mature over time, where they age and suffer
mutations throughout their lives. In reproduction, couples match by mutual
attraction, where they may have offspring. Death can happen to everyone: from a
newborn to an aged adult, where the individual's fitness will impact their
longevity. As a proof-of-concept, we implemented the algorithm with Docker
containers by solving the OneMax problem comparing it with a basic (sequential) GA 
algorithm, where it showed favorable and promising results.

>>>>

Several bio-inspired algorithms use population evolution as analogies of
nature. In this paper, we followed a strategy that takes a similar approach as
the study of bacteria growth in microbiology, where using a microscope, we can
observe and analyze the evolution of a population over time. We present an
algorithm inspired by the biological life-cycle of animal species, which
consists of several stages: birth, growth, reproduction, and death. As in
nature, we intend to execute all these stages in parallel and asynchronously on
a population that evolves constantly.

In this paper, we present a novel distributed nature-inspired algorithm for
solving optimization problems. From the ground up, we designed the algorithm as
a cloud-native solution using the cloud available resources to divide the
processing work-load, among several computers or running the algorithm as a
cloud service. The algorithm works concurrently and asynchronously on a
constantly evolving population, using different computers (or containers)
independently, eliminating waiting times between processes.

This algorithm seeks to imitate the natural life cycle, where new individuals
are born at any moment and mature over time, where they age and suffer
mutations throughout their lives. In reproduction, couples match by mutual
attraction, where they may have offspring. Death can happen to everyone: from a
newborn to an aged adult, where the individual's fitness will impact their
longevity. As a proof-of-concept, we implemented the algorithm with Docker
containers by solving the OneMax problem comparing it with a basic GA
(sequential) algorithm, where it showed favorable and promising results.
